The Negative Effect of Traffic Noise on House Prices: A Landscape Hedonic Analysis

### 2013-09-30 reports/Draft.tex
another round of editing, updated correlation matrix, etc.

\subsection{Time}
Given that we have data from before and after the recession of 2008-09, we subset the data in Table \ref{tab:SumStatsTime} by year of sale to look for differences over time. In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years. For example, in 2010 there were only 4,206 property sales within the dataset, less than half as many in 2005. While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years. However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).

\begin{table}
\caption{Mean Variable Values Across Time}\label{tab:SumStatsTime}
\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
\end{table}

@@

\begin{table}[bp]
\caption{Hedonic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)} \label{tab:mainresults} 
\makebox[\linewidth]{
\small
\begin{tabular}{lrrrrrr} \\
 & \multicolumn{2}{c}{Global Model} & \multicolumn{4}{c}{Locally Weighted Regression Model} \\
 & \multicolumn{1}{c}{$\hat{\beta}$} & \multicolumn{1}{c}{$\hat{\sigma}_{\hat{\beta}}$} & mean $\hat{\beta}$ & \multicolumn{1}{c}{$\sigma_{\hat{\beta}}$} & (5) & (6) \\ 
  \hline
(Intercept) & 8.4E+00 & 1.3E-01 & 2.9E+00 & 1.5E+01 & 0.64 & 0.00 \\ 
  Traffic Noise & -2.6E-03 & 1.6E-04 & -2.5E-03 & 3.0E-03 & 0.47 & 0.67 \\ 
  House Size & 3.0E-04 & 2.7E-06 & 2.6E-04 & 9.1E-05 & 1.00 & 0.00 \\ 
  Lot Size & 2.6E-01 & 1.5E-02 & 4.0E-01 & 3.7E-01 & 0.67 & 0.00 \\ 
  Year of Construction & 1.2E-03 & 6.5E-05 & 4.5E-03 & 5.4E-03 & 0.79 & 0.00 \\ 
  Owner Occupancy & 2.7E-02 & 3.2E-03 & 2.3E-02 & 6.4E-02 & 0.37 & 1.00 \\ 
  Elementary Test Scores & 1.5E-03 & 1.2E-04 & 2.4E-04 & 3.1E-02 & 0.30 & 0.00 \\ 
  Median Income & 3.3E-06 & 7.7E-08 & 9.6E-07 & 8.1E-06 & 0.35 & 0.00 \\ 
  distance to CBD & 1.3E-05 & 6.3E-07 & 1.1E-05 & 1.0E-04 & 0.30 & 0.00 \\ 
  `` nearest Park & -3.7E-07 & 1.1E-06 & -1.6E-05 & 1.3E-04 & 0.32 & 0.00 \\ 
  `` nearest Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
  `` nearest Shop & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
  location of sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
  timing of sale & \multicolumn{2}{c}{year fixed effects} & \multicolumn{4}{c}{within last 12 months} \\
 \hline
  GCV score & \multicolumn{2}{c}{0.041} & \multicolumn{2}{c}{0.027}  &  & \\
  Moran's I statistic & \multicolumn{2}{c}{0.199} & \multicolumn{2}{c}{0.012} & & \\
\end{tabular}
}
 \caption*{\footnotesize Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
\end{table}

The first column in Table \ref{tab:mainresults} displays the estimates from a standard semi-log OLS regression with traffice noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables. The coefficient in the second row of the table shows the estimated impact of an additional dB of traffic noise on the natural log of the house sale price to be -.23 percent. This value is within the range of other estimates as described earlier in section \ref{sec:lit}. Coefficients for the dummy variables (on house style, city, and year of sale) are not reported for the sake of brevity, but are available upon request. The second column in the table reports the estimated coefficient standard errors. With the exception of the coefficient on the distance to the nearest park, all reported coefficients are statistically different from zero at conventional levels.

The third column displays the mean estimated coefficients from the LWR model. In this model coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months. The fourth column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques.

@@

\subsection{Does the Hedonic Function Vary over Space?}
We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}. In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data. In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales just as before. In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth. The smallest of these GCV scores was 0.041, just as was the case with the global (non-LWR) model. In other words, after running thousands of regressions on the shuffled data, we never obtained model performance anywhere near the LWR model with our true locational data. This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.

In the previous simulation we found that the hedonic regression function indeed exhibits spatial non-stationarity. However, we have not yet established which variables have spatially varying coefficients. In the second simulation, we seek to explore which of the hedonic regression coefficients exhibit spatial non-stationarity. We repeat the Monte Carlo simulation described earlier, but only at the optimal bandwidth from the original LWR model. We collected the standard deviation of the estimated LWR coefficients for each variable in each iteration of the simulation. The intuition of the simulation is as follows: a variable might truly exert a spatially stationary effect on house prices, but our estimates vary over space due to chance. If this is the case, by shuffling the location of our observations and rerunning the LWR model, we should see a similar dispersion in regression coefficients over space. However, if the coefficient exhibits true spatial non-stationarity, it is unlikely that we will see as large of a standard deviation in the coefficient estimates after having reshuffled the data (because now the houses for which a coefficient exerts a strong effect are now no longer near each other).

After $M = 100$ iterations of this simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data. The fourth column in Table \ref{tab:mainresults} displays the standard deviations of the LWR regression coefficients obtained with our data. Column (6) displays the proportion of Monte Carlo simulatons that yielded larger standard deviations of LWR coefficient estimates than those shown in column (4). For most variables, we never obtained a larger coefficient standard deviation in the simulation than we obtained from the LWR model with the actual data. However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients in our data may have been due to random chance. These coefficients may in fact be stationary across the study area, while the other coefficients appear to be non-stationary. Future work may want to estimate a mixed-LWR model in which the coefficients on traffic noise and owner occupancy remain stationary while the other coefficients are allowed to vary over space. See \citet{Fotheringham2002} for a description of a mixed-LWR estimation algorithm.

Figure \ref{fig:MCsds} visually shows the results presented in column (6) of Table \ref{tab:mainresults} another way. Each subfigure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red). Note that it is the case that the standard deviations obtained with the actual data are substantially larger than those obtained in the simulation for most of the variables.

\begin{figure}
 \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDsClean}}
 \caption{Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.}\label{fig:MCsds}
\end{figure}

In addition to the LWR model with a bandwidth of the nearest 200 houses and a temporal lag of 12 months performing better than other bandwidths and model specifications in terms of the smallest GCV score, it also exhibits far less spatial autocorrelation within the model residuals. We calculate the Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification reduces the Moran's I statistic to 0.012, a nearly twenty-fold reduction.

@@

Previous research has suggested that the impact of noise can change with time and economic conditions. For instance, \citet{Wilhelmsson2000} found that the traffic noise penalty to be stronger in the 1990s near Stockholm, Sweden compared to the 1980s. \citet{Cohen2009} also found the (airport) noise penalty to be larger in the early 2000s compared to the late 1990s in Atlanta, Georgia. We know that house prices in the United States fell dramatically during and after the Great Recession of 2008-09. We know less about the patterns of change in the hedonic price functions during and after the fall in prices. \citet{Cho2011b} found evidence from hedonic analysis in the Nashville, Tennessee area that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.

In this section we look for evidence of temporal non-stationarity in the hedonic coefficient on traffic noise within our data. Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}'' for all sales after September 2008. We then regress our LWR noise coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction}, 
\begin{equation}\label{eq:LWRinteraction}
\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*Month} + \alpha _2  \texttt{*Post} + \alpha _3 \texttt{*Post*Month} + \epsilon.
\end{equation}
The results of this regression will help us understand the patterns of change in the implicit price of traffic noise. In particular, $\alpha_1 \neq 0$ suggests a linear temporal trend in the marginal willingness to pay to avoid traffic noise, while $\alpha_2 \neq 0$ suggests that there was a structural break after September 2008, and $\alpha_3 \neq 0$ will imply a change in the temporal trend after September 2008. The linear regression results presented in Table \ref{tab:betaMAX} show that there is a significant negative shock to the estimated LWR coefficients for traffic noise after September 2008. Additionally, the coefficients also begin to a significant negative trend.
\begin{table}[htb]
\caption{Dependent Variable = Traffic Noise LWR Coefficients}\label{tab:betaMAX}
\begin{center}
\begin{tabular}{lrrr}
           & Estimate & Std.\ Err. & t-stat  \\  \hline
(Intercept) & -1.7e-03 &  4.1e-05 &  -43.4   \\
Month       & 6.9e-06 &  2.0e-06  &   3.5    \\
Post        &-8.0e-04 &  7.2e-05  & -11.1    \\
Month*Post  &-8.9e-05 &  4.5e-06  & -19.7    \\ \hline
%\multicolumn{5}{l}{Residual standard error: 0.0028 with df = 31,744} \\
\multicolumn{4}{l}{R$^2$: 0.093,  Adjusted R$^2$: 0.093} \\
%\multicolumn{4}{l}{Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
\end{tabular}
\end{center}
\end{table}

The results in Table \ref{tab:betaMAX} contradict the a priori expectation that environmental amenities will ``matter'' less during and after the Great Recession compared to the housing boom. In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise increased. That is, the negative hedonic coefficients on traffic noise got more negative after September 2008. It should be noted that our simple model can explain almost 10 percent of the variation in traffic noise LWR coefficient estimates.

% \subsubsection{House Size}
% 
% In this section we show how the hedonic coefficients on house size (as measured in square feet) change over time. Table \ref{tab:betaSQFT} shows that the LWR coefficients on house size were positive and trending up before September 2008, then the coefficients drop significantly in both absolute value and their time trend. These results are consistent with the belief that the Great Recession would reduce consumer's marginal willingness to pay for increases in the size of a house. It should be noted that the model presented in Table \ref{tab:betaSQFT} explains less than one percent of the variation in our house size LWR coefficients.
% 
% \begin{table}[h]
% \caption{Regression Results: Dependent Variable = House Size LWR Coefficients}\label{tab:betaSQFT}
% \begin{verbatim}
%               Estimate Std. Error t value Pr(>|t|)    
% (Intercept)  2.741e-04  1.317e-06 208.097  < 2e-16 ***
% month        8.742e-07  6.441e-08  13.573  < 2e-16 ***
% Post        -1.678e-05  2.316e-06  -7.245 4.43e-13 ***
% month:Post  -5.989e-07  1.440e-07  -4.157 3.23e-05 ***
% ---
% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
% 
% Residual standard error: 9.04e-05 on 31744 degrees of freedom
% Multiple R-squared: 0.006092,  Adjusted R-squared: 0.005998 
% F-statistic: 64.85 on 3 and 31744 DF,  p-value: < 2.2e-16 
% \end{verbatim}
% \end{table}
% 
% \subsubsection{Lot Size}
% 
% Table \ref{tab:betaACRES} shows interesting results that are qualitatively different from our previous results. The post-September 2008 dummy variable coefficient is only marginally significant and small in absolute value (when compared to the regression Intercept term). There is no discernable change in the temporal trend of the lot size LWR coefficients. The model presented in Table \ref{tab:betaACRES} explains less than a half of one percent of the variation in lot size LWR coefficients.
% 
% \begin{table}[h]
% \caption{Regression Results: Dependent Variable = Lot Size LWR Coefficients}\label{tab:betaACRES}
% \begin{verbatim}
% (Intercept)  0.3828690  0.0054089  70.785  < 2e-16 ***
% month       -0.0015113  0.0002645  -5.713 1.12e-08 ***
% Post         0.0190349  0.0095117   2.001   0.0454 *  
% month:Post  -0.0001358  0.0005916  -0.229   0.8185    
% ---
% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
% 
% Residual standard error: 0.3713 on 31744 degrees of freedom
% Multiple R-squared: 0.002806,  Adjusted R-squared: 0.002711 
% F-statistic: 29.77 on 3 and 31744 DF,  p-value: < 2.2e-16 
% \end{verbatim}
% \end{table}
% 
% \subsubsection{Intercept}
% We were also interested in how the LWR regression intercept changed over time. For instance, perhaps the house price drops of the Great Recession were manifested primarily through reduced intercept terms. Table \ref{tab:betaINT} is not consistent with that hypothesis. In fact, our results show that the estimated LWR intercept terms are on average significantly higher post-September 2008.
% \begin{table}[h]
% \caption{Regression Results: Dependent Variable = LWR Intercept Estimates}\label{tab:betaINT}
% \begin{verbatim}
% (Intercept)  1.575488   0.213779   7.370 1.75e-13 ***
% month       -0.043836   0.010455  -4.193 2.76e-05 ***
% Post         2.845774   0.375939   7.570 3.84e-14 ***
% month:Post   0.007397   0.023383   0.316    0.752    
% ---
% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
% 
% Residual standard error: 14.67 on 31744 degrees of freedom
% Multiple R-squared: 0.003282,  Adjusted R-squared: 0.003188 
% F-statistic: 34.84 on 3 and 31744 DF,  p-value: < 2.2e-16  
% \end{verbatim}
% \end{table}

\subsection{Does the Impact of Traffic Noise Vary Non-linearly?}

@@

\begin{table}
\begin{center}
\caption{LWR Noise Coefficients vs.\ Noise Levels}\label{tab:LWRnonlinear}
\begin{tabular}{lrrr}
         &   Estimate & Std.\ Err. & t-value \\ \hline
(Intercept) & -1.8e-03 & 1.3e-04  &-13.3 \\
Noise       & -2.8e-06 & 2.3e-06  & -1.2 \\  
Post        & -3.6e-03 & 2.2e-04  &-16.2 \\
Noise:Post  &  3.4e-05 & 4.0e-06  &  8.5 \\ \hline
%\multicolumn{4}{Residual standard error: 0.003 with df = 31,744}
\multicolumn{4}{l}{R$^2$: 0.083,  Adjusted R$^2$: 0.083} 
%F-statistic: 961.4 on 3 and 31744 DF,  p-value: < 2.2e-16 
\end{tabular}
\end{center}
\end{table}

@@

Our work suffers from at least two noticeable weaknesses. First, we are missing some important structural variables that are commonly used in the housing hedonic literature. To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality covary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias. We are somewhat comforted, however, because we do have some additional variables for a subset of our data. We obtained the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office. Our analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted. We found strikingly similar estimates of the impact of traffic noise.

\begin{table}[ht]
\begin{center}
\caption{A Comparison of the Noise Regression Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
\begin{tabular}{lllc}
 & \multicolumn{2}{p{1.25in}}{Additional Variables Included in LWR?} & \\
Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} & \\ \cline{1-3}
\multirow{2}{*}{Model (1) = Structural Variables} & -0.0015 & -0.0015 & mean\\ 
   & (0.0023) & (0.0031) & (st.\ dev.) \\[.2cm]
\multirow{2}{*}{Model (2) = Model (1) + Locational Variables} & -0.0014 & -0.0014  & \\ 
   & (0.0018) & (0.0022) &  \\[.2cm] 
\multirow{2}{*}{Model (3) = Model (2) + City Fixed Effects} & -0.0014 & -0.0014 & \\ 
   & (0.0022) & (0.0018) & \\ 
\end{tabular}
\end{center}
\end{table}

>>>>

\subsection{Time}
Given that we have data from before and after the recession of 2008-09, we subset the data in Table \ref{tab:SumStatsTime} by year of sale to look for differences over time. In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years. For example, in 2010 there were only 4,206 property sales within the dataset, less than half as many in 2005. While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years. However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from over 58 dB to less than 53 dB).

\begin{table}
\begin{center}
\caption{Mean Variable Values by Year}\label{tab:SumStatsTime}
\small
%\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
% Table generated by Excel2LaTeX from sheet 'Descriptive StatisticsYear'
    \begin{tabular}{lrrrrrr|r}
    Variable & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2005-10\\ \hline
    Sales Value (\$1000s) & 279   & 282   & 275   & 263   & 231   & 233   & 266 \\
    House Size (ft$^2$) & 1737  & 1736  & 1743  & 1813  & 1727  & 1775  & 1750 \\
    Lot Size (acres) & 0.25  & 0.25  & 0.25  & 0.26  & 0.25  & 0.26  & 0.25 \\
    Year Built  & 1967  & 1966  & 1966  & 1971  & 1968  & 1968  & 1967 \\
    Traffic Noise (dB) & 58.5  & 58.6  & 58.6  & 52.5  & 52.8  & 52.8  & 56.4 \\
    Median Income (\$1000s) & 72.0  & 72.1  & 72.3  & 74.8  & 72.6  & 73.2  & 72.6 \\
    Elem. Test Scores & 364.8 & 364.8 & 365.2 & 363.5 & 362.3 & 366.1 & 364.5 \\
    Dist. to CBD (km) & 14.7  & 14.6  & 14.8  & 15.0  & 14.3  & 14.5  & 14.7 \\
    Dist. to Park (km) & 2.6   & 2.6   & 2.6   & 2.8   & 2.6   & 2.6   & 2.6 \\
    Dist. to Lake (km) & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9 \\
    Dist. to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
    Number of Observations &  10,991  & 8,885  &  6,549  &
    \end{tabular}%
\end{center}
\end{table}

@@

\begin{table}[bp]
\caption{Hedonic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)} \label{tab:mainresults} 
\makebox[\linewidth]{
\small
\begin{tabular}{lrrrrrr} \\
 & \multicolumn{2}{c}{Global Model} & \multicolumn{4}{c}{Locally Weighted Regression Model} \\
 & \multicolumn{1}{c}{$\hat{\beta}$} & \multicolumn{1}{c}{$\hat{\sigma}_{\hat{\beta}}$} & mean $\hat{\beta}$ & \multicolumn{1}{c}{$\sigma_{\hat{\beta}}$} & (5) & (6) \\ 
  \hline
(Intercept) & 8.4E+00 & 1.3E-01 & 2.9E+00 & 1.5E+01 & 0.64 & 0.00 \\ 
  Traffic Noise & -2.6E-03 & 1.6E-04 & -2.5E-03 & 3.0E-03 & 0.47 & 0.67 \\ 
  House Size & 3.0E-04 & 2.7E-06 & 2.6E-04 & 9.1E-05 & 1.00 & 0.00 \\ 
  Lot Size & 2.6E-01 & 1.5E-02 & 4.0E-01 & 3.7E-01 & 0.67 & 0.00 \\ 
  Year Built & 1.2E-03 & 6.5E-05 & 4.5E-03 & 5.4E-03 & 0.79 & 0.00 \\ 
  Owner Occupancy & 2.7E-02 & 3.2E-03 & 2.3E-02 & 6.4E-02 & 0.37 & 1.00 \\ 
  Elem.\ Test Scores & 1.5E-03 & 1.2E-04 & 2.4E-04 & 3.1E-02 & 0.30 & 0.00 \\ 
  Median Income & 3.3E-06 & 7.7E-08 & 9.6E-07 & 8.1E-06 & 0.35 & 0.00 \\ 
  Dist.\ to CBD & 1.3E-05 & 6.3E-07 & 1.1E-05 & 1.0E-04 & 0.30 & 0.00 \\ 
  Dist.\ to Park & -3.7E-07 & 1.1E-06 & -1.6E-05 & 1.3E-04 & 0.32 & 0.00 \\ 
  Dist.\ to Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
  Dist.\ to Shop & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
  Location of Sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
  Timing of Sale & \multicolumn{2}{c}{year fixed effects} & \multicolumn{4}{c}{within last 12 months} \\
 \hline
  GCV score & \multicolumn{2}{c}{0.041} & \multicolumn{2}{c}{0.027}  &  & \\
  Moran's I statistic & \multicolumn{2}{c}{0.199} & \multicolumn{2}{c}{0.012} & & \\
\end{tabular}
}
 \caption*{\footnotesize Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
\end{table}

Table \ref{tab:mainresults} presents the results of our preferred LWR model as well as a basic global OLS model for comparison. The first two columns display the estimates and standard errors from a basic semi-log OLS regression with traffic noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables. The third column displays the mean estimated coefficients from the LWR model. In this model coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months. The fourth column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques. In addition to the significant reduction in the GCV score (0.041 vs. 0.027) obtained with the use of LWR, we also see a substantal reduction in the degree of spatial autocorrlation in the model residuals. We calculate the Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification reduces the Moran's I statistic to 0.012, a nearly twenty-fold reduction.

@@

\subsection{Does the Hedonic Function Vary over Space?}
We believe the hedonic function varies significantly over space and the use of a LWR estimation procedure is appropriate. We conducted two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}. In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data. In both cases the results strongly suggest spatial non-stationarity in the hedonic function.

In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales just as before. In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth. The smallest of these GCV scores was 0.041, just as was the case with the global (non-LWR) model. In other words, after running thousands of regressions on the shuffled data, we never obtained model performance anywhere near the LWR model with our true locational data. This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.

In the previous simulation we found that the hedonic regression function indeed exhibits spatial non-stationarity. However, we have not yet established which variables have spatially varying coefficients. In the second simulation, we seek to explore which of the hedonic regression coefficients exhibit spatial non-stationarity. We repeat the Monte Carlo simulation described earlier, but only at the optimal bandwidth from the original LWR model. We collected the standard deviation of the estimated LWR coefficients for each variable in each iteration of the simulation. The intuition of this simulation is as follows: a variable might truly exert a spatially \emph{stationary} effect on house prices, but our estimates vary over space due to chance. If this is the case, by shuffling the location of our observations and rerunning the LWR model, we should see a similar dispersion in regression coefficients over space with the reshuffled data as with our actual data. However, if the coefficient exhibits true spatial \emph{non-stationarity}, it is unlikely that we will see such a large of a standard deviation in the coefficient estimates after having reshuffled the data (because now the houses for which a coefficient exerts a strong effect are probably no longer near each other).

After 100 iterations of this second simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data. The fourth column in Table \ref{tab:mainresults} displays the standard deviations of the LWR regression coefficients obtained with our data. Column (6) displays the proportion of Monte Carlo simulatons that yielded larger standard deviations of LWR coefficient estimates than those shown in column $\sigma_{\hat{\beta}}$. For most variables, we never obtained a larger standard deviation in the simulation than we obtained from the LWR model with the actual data. However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients in our data may have been due to random chance. These coefficients may in fact be stationary across the study area, while the other coefficients appear to be non-stationary. Future work may want to estimate a mixed-LWR model in which the coefficients on traffic noise and owner occupancy remain stationary while the other coefficients are allowed to vary over space. See \citet{Fotheringham2002} for a description of a mixed-LWR estimation algorithm.

Figure \ref{fig:MCsds} visualizes the results of the second simulation. Each subfigure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red). Note that it is the case that the standard deviations obtained with the actual data are typically substantially larger than those obtained in the simulation for most of the variables. However, the variation obtained in the traffic noise coefficients simulations is similar with our actual LWR results, suggesting that the spatial non-stationarity exhibited in this coefficient is likely due to chance and not true spatial non-stationarity in the effect of traffic noise on house prices.

\begin{figure}
 \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDsClean}}
 \caption{Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable. Figures in which the red line is to the right of the black distribution suggest spatial non-stationarity in effect of the variable on house prices in our study region.}\label{fig:MCsds}
\end{figure}

The results of these simulations suggest that spatial non-stationarity exists in the hedonic function and that LWR techniques are able to capture a significant portion of the non-stationarity. Using a bandwidth of the nearest 200 houses and a temporal lag of 12 months not only yielded significantly smaller GCV scores compared to other bandwidths and model specifications, but such performance does not seem to be a result of a chance spatial arrangement of the data.

@@

Previous research has suggested that the impact of noise can change with time and economic conditions. For instance, \citet{Wilhelmsson2000} found that the traffic noise penalty to be stronger in the 1990s near Stockholm, Sweden compared to the 1980s. \citet{Cohen2009} also found the (airport) noise penalty to be larger in the early 2000s compared to the late 1990s in Atlanta, Georgia. We know that house prices in the United States fell dramatically during and after the Great Recession of 2008-09. We know less about the patterns of change in the hedonic price functions during and after the fall in house prices. \citet{Cho2011b} found evidence from hedonic analysis in Nashville, Tennessee,  that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.

In this section we look for evidence of temporal non-stationarity in the hedonic coefficient on traffic noise within our data. Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}=1'' for all sales after September 2008. We then regress our LWR noise coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction}, 
\begin{equation}\label{eq:LWRinteraction}
\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*Month} + \alpha _2  \texttt{*Post} + \alpha _3 \texttt{*Post*Month} + \epsilon.
\end{equation}
The results of this regression will help us understand the patterns of change in the implicit price of traffic noise. In particular, $\alpha_1 \neq 0$ suggests a linear temporal trend in the marginal willingness to pay to avoid traffic noise, while $\alpha_2 \neq 0$ suggests that there was a structural break after September 2008, and $\alpha_3 \neq 0$ will imply a change in the temporal trend after September 2008. The linear regression results presented in Table \ref{tab:betaMAX} show that there the estimated LWR coefficients for traffic noise are significantly smaller after September 2008.
\begin{table}[htb]
\caption{Dependent Variable = Traffic Noise LWR Coefficients}\label{tab:betaMAX}
\begin{center}
\begin{tabular}{lrrr}
           & Estimate & Std.\ Err. & t-stat  \\  \hline
(Intercept) & -1.7e-03 &  4.1e-05 &  -43.4   \\
Month       & 6.9e-06 &  2.0e-06  &   3.5    \\
Post        &-8.0e-04 &  7.2e-05  & -11.1    \\
Month*Post  &-8.9e-05 &  4.5e-06  & -19.7    \\ \hline
\multicolumn{4}{l}{Residual standard error: 0.003} \\
\multicolumn{4}{l}{N = 31,748, R$^2$: 0.093} \\ %,  Adjusted R$^2$: 0.093
%\multicolumn{4}{l}{Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
\end{tabular}
\end{center}
\end{table}

The results in Table \ref{tab:betaMAX} contradict the expectation that environmental amenities will ``matter'' less during and after the Great Recession compared to the housing boom. In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise became more severe. That is, the negative hedonic coefficients on traffic noise got more negative after September 2008.

\subsection{Are There Threshold Effects of Traffic Noise?}

@@

\begin{table}
\begin{center}
\caption{LWR Noise Coefficients vs.\ Noise Levels}\label{tab:LWRnonlinear}
\begin{tabular}{lrrr}
         &   Estimate & Std.\ Err. & t-value \\ \hline
(Intercept) & -1.8e-03 & 1.3e-04  &-13.3 \\
Noise       & -2.8e-06 & 2.3e-06  & -1.2 \\  
Post        & -3.6e-03 & 2.2e-04  &-16.2 \\
Noise*Post  &  3.4e-05 & 4.0e-06  &  8.5 \\ \hline
\multicolumn{4}{l}{Residual standard error: 0.003} \\
\multicolumn{4}{l}{N: 31,748, R$^2$: 0.083} \\
%F-statistic: 961.4 on 3 and 31744 DF,  p-value: < 2.2e-16 
\end{tabular}
\end{center}
\end{table}

@@

The hedonic analysis results presented suggest that traffic noise exhibits a significant negative effect on house prices and that the hedonic function varies over space and time. These results and analysis rest on important assumptions, which if violated, may change the results. This section describes two assumptions that we think are most noteworthy of discussion: lack of omitted variable bias and temporal non-stationarity in the level of several variables across the region during our study period.

Our data lack some important structural variables that are commonly used in the housing hedonic literature. To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality covary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias. We are somewhat comforted, however, because we do have some additional variables for a subset of our data. We obtained the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office. Our analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted. We found strikingly similar estimates of the impact of traffic noise.

\begin{table}[ht]
\begin{center}
\caption{Noise Regression Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
\begin{tabular}{lll}
 & \multicolumn{2}{p{1.25in}}{Additional Variables Included in LWR?} \\
Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} \\ \cline{1-3}
\multirow{2}{*}{Model (1) = Structural Variables} & -0.0015 & -0.0015 \\ 
   & (0.0023) & (0.0031)  \\[.2cm]
\multirow{2}{*}{Model (2) = Model (1) + Locational Variables} & -0.0014 & -0.0014  \\ 
   & (0.0018) & (0.0022)  \\[.2cm] 
\multirow{2}{*}{Model (3) = Model (2) + City Fixed Effects} & -0.0014 & -0.0014 \\ 
   & (0.0022) & (0.0018) \\[.2cm] \cline{1-3}
\multicolumn{3}{p{4.25in}}{Mean and (standard deviation) LWR traffic noise coefficients when the number of bedrooms, bathrooms, and garage size are included as additional control variables in the regression.}
\end{tabular}
\end{center}
\end{table}
